Preprocessing

### 2023-09-07 analysis/preprocessing.Rmd
Update preprocessing.Rmd

```{r}
# create exclusion_final column
d_articles <- d_articles %>%
  mutate(exclusion_final = case_when(
    sample_id == 'random' & article_id == '37' ~ exclusion_primary,
    sample_id == 'random' & article_id == '41' ~ exclusion_primary,
    sample_id == 'random' & article_id == '68' ~ exclusion_secondary,
    sample_id == 'random' & article_id == '95' ~ exclusion_secondary,
    sample_id == 'random' & article_id == '103' ~ exclusion_primary,
    sample_id == 'random' & article_id == '120' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '30' ~ exclusion_secondary,
    sample_id == 'prominent' & article_id == '49' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '66' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '98' ~ exclusion_primary,
    TRUE ~ exclusion_primary
  ))

# create exclusion_reason_final column
d_articles <- d_articles %>%
  mutate(exclusion_reason_final = case_when(
    sample_id == 'random' & article_id == '37' ~ exclusion_reason_primary,
    sample_id == 'random' & article_id == '41' ~ exclusion_reason_primary,
    sample_id == 'random' & article_id == '68' ~ exclusion_reason_secondary,
    sample_id == 'random' & article_id == '95' ~ exclusion_reason_secondary,
    sample_id == 'random' & article_id == '103' ~ exclusion_reason_primary,
    sample_id == 'random' & article_id == '120' ~ exclusion_reason_primary,
    sample_id == 'prominent' & article_id == '30' ~ exclusion_reason_secondary,
    sample_id == 'prominent' & article_id == '49' ~ exclusion_reason_primary,
    sample_id == 'prominent' & article_id == '66' ~ exclusion_reason_primary,
    sample_id == 'prominent' & article_id == '98' ~ exclusion_reason_primary,
    TRUE ~ exclusion_reason_primary
  ))
```

@@

```{r}
# we've already dealt with cases where the decision to exclude differs, so we're not looking only at cases where the decision to exclude matches, but the reason for exclusion differs
# d_articles %>% # NOT RUN
#   filter(exclusion_primary == exclusion_secondary, 
#          exclusion_reason_primary != exclusion_reason_secondary) %>%
#   select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary)
```

>>>>

```{r}
# create exclusion_final column
d_articles <- d_articles %>%
  mutate(exclusion_final = case_when(
    sample_id == 'random' & article_id == '37' ~ exclusion_primary,
    sample_id == 'random' & article_id == '41' ~ exclusion_primary,
    sample_id == 'random' & article_id == '68' ~ exclusion_secondary,
    sample_id == 'random' & article_id == '95' ~ exclusion_secondary,
    sample_id == 'random' & article_id == '103' ~ exclusion_primary,
    sample_id == 'random' & article_id == '120' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '30' ~ exclusion_secondary,
    sample_id == 'prominent' & article_id == '49' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '66' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '98' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '123' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '124' ~ exclusion_primary,
    sample_id == 'prominent' & article_id == '130' ~ exclusion_secondary,
    sample_id == 'prominent' & article_id == '132' ~ exclusion_primary,
    TRUE ~ exclusion_primary
  ))

# create exclusion_reason_final column
d_articles <- d_articles %>%
  mutate(exclusion_reason_final = case_when(
    sample_id == 'random' & article_id == '37' ~ exclusion_reason_primary,
    sample_id == 'random' & article_id == '41' ~ exclusion_reason_primary,
    sample_id == 'random' & article_id == '68' ~ exclusion_reason_secondary,
    sample_id == 'random' & article_id == '95' ~ exclusion_reason_secondary,
    sample_id == 'random' & article_id == '103' ~ exclusion_reason_primary,
    sample_id == 'random' & article_id == '120' ~ exclusion_reason_primary,
    sample_id == 'prominent' & article_id == '30' ~ exclusion_reason_secondary,
    sample_id == 'prominent' & article_id == '49' ~ exclusion_reason_primary,
    sample_id == 'prominent' & article_id == '66' ~ exclusion_reason_primary,
    sample_id == 'prominent' & article_id == '98' ~ exclusion_reason_primary,
    sample_id == 'prominent' & article_id == '130' ~ exclusion_reason_secondary,
    TRUE ~ exclusion_reason_primary
  ))
```

@@

```{r}
# we've already dealt with cases where the decision to exclude differs, so we're not looking only at cases where the decision to exclude matches, but the reason for exclusion differs
 # d_articles %>% # NOT RUN
 #   filter(exclusion_primary == exclusion_secondary, 
 #          exclusion_reason_primary != exclusion_reason_secondary) %>%
 #   select(article_id, sample_id, exclusion_reason_primary, exclusion_reason_secondary, exclusion_reason_final)
```
